---
output:
  pdf_document: default
  html_document: default
---

### For the following data frame:
```{r}
data("mtcars")
head(mtcars)
```
# Keep in mind the following...
```{r}

x <- 1:10 # create vector
x >= 3 # greater than or equal to
x < 9 # less than 9
x > 3 & x < 7 # greater than 3 AND less than 7
x >= 9 | x <= 2 # greater than or equal to 9 OR less than or equal to 2
x %in% 5:10 # present in a given set
x == 3 # equal to 3
x != 3 # not equal to 3
x %% 2 == 0 # modulo division (does remainder equal 0 when divided by 2)
xor(x == 3, x > 1) # matches ONLY ONE of the conditions...NOT BOTH
```


## Exercise 1
Use logical operators to output only those rows of  mtcars  where column  mpg  is between 15 and 20 (excluding 15 and 20).
```{r}
mtcars[mtcars$mpg > 15 | mtcars$mpg < 20, ]
```
## Exercise 2
Use logical operators to output only those rows of  mtcars  where column  cyl  is equal to 6 and column  am  is not 0.

```{r}
mtcars[mtcars$cyl == 6 & mtcars$am != 0, ]
```

## Exercise 3
Use logical operators to output only those rows of  mtcars  where column  gear  or  carb  has the value 4.
```{r}
mtcars[mtcars$carb == 4 | mtcars$gear ==4, ]
```

## Exercise 4
Use logical operators to output only the even rows of  mtcars.
```{r}
mtcars[row(mtcars) %% 2 == 0, ]
```

## Exercise 5
Use logical operators and change every fourth element in column  mpg  to 0.
```{r}
mtcars$mpg[seq_len(nrow(mtcars))%%4 == 0] <- 0
```

## Exercise 6
Output only those rows of  mtcars  where columns  vs  and  am  have the same value 1, solve this without using  ==  operator.
```{r}
mtcars[mtcars$vs != 0 & mtcars$am!= 0, ]
```

## Exercise 7
(TRUE + TRUE) * FALSE , what does this expression evaluate to and why?
```{r}
(TRUE + TRUE) * FALSE
(1 + 1) * 0
```

## Exercise 8
Output only those rows of  mtcars  where at least  vs  or  am  have the value 1, solve this without using  ==  or  !=.
```{r}
mtcars[mtcars$vs & mtcars$am, ]
```

## Exercise 9
Explain the difference between  | ,  || ,  &  and  &&.
```{r}
c1 <- c(TRUE, TRUE, FALSE, FALSE)
c2 <- c(TRUE, FALSE, TRUE, FALSE)
c1 | c2
c1[4] || c2[4]
c1 & c2
c1[4] && c2[4]

```

## Exercise 10
Change all values that are 0 in the column  am  in  mtcars  to 2.
```{r}
mtcars$am[mtcars$am == 0] <- 2
mtcars$am
```

## Exercise 11
Add 2 to every element in the column  vs  without using numbers.
```{r}
mtcars$vs <- mtcars$vs + max(mtcars$am)
```

## Exercise 12
Output only those rows of  data  where  vs  and  am  have different values, solve this without using  ==  or  !=.
```{r}
mtcars[!is.na(mtcars$vs - mtcars$am),  ]
```
